Distances between histograms

### 2015-10-28 paper.tex
feito benchmarking de diferencas

% Input tables
% any plot? If std is ~stable, plots of the mean of c~(\alpha) are compact and informative
\input{tables/tabNormNull}
\input{tables/tabUniformNull}
\input{tables/tabWeibullNull}
% distribuicoes normal, uniforme, weibul
% distribuicao de lei de potencia
% contemplar numeros diferentes de bins, de amostras e de distribuicoes
% enquanto mantemos mudando os parametros
\section{References in empirical data}\label{sec:empirical}
% nltk com machado, shakespeare e biblia
% arquivo de audio
% bytes quaisquer de algum arquivo?
% dados puxados da wikipedia, gmane ou ?
\section{Conclusions}\label{sec:conc}
\begin{acknowledgments}
	Financial support was obtained from CNPq (140860/2013-4,
	project 870336/1997-5), United Nations Development Program (contract: 2013/000566; project BRA/12/018) and FAPESP. 
	The authors are grateful to the American Jewish Committee for maintaining an online copy of the Adorno book used on the epigraph~\cite{adorno}, to GMANE creators and maintainers for the public email list data, to the communities of the email lists and other groups used in the analysis, and to the Brazilian Presidency of the Republic for keeping Participabr code and data open.
	We are also grateful to developers and users of Python scientific tools.
\end{acknowledgments}

>>>>

% Input tables
% any plot? If std is ~stable, plots of the mean of c~(\alpha) are compact and informative
\input{tables/tabNormNull}
\input{tables/tabUniformNull}
\input{tables/tabWeibullNull}

\subsection{When the null hypothesis if false}
The $m(c')$ are median values of $c'$.
$\overline{C'(\alpha)}=\frac{|C'(\alpha)|}{N_c}$ is the fraction
of rejection of the null hypothesis with critical region $\alpha$.
\input{tables/tabNormDiff3}
%\input{tables/tabNormDiff1}
%\input{tables/tabNormDiff2}

% distribuicoes normal, uniforme, weibul
% distribuicao de lei de potencia
% contemplar numeros diferentes de bins, de amostras e de distribuicoes
% enquanto mantemos mudando os parametros
\section{Example uses in empirical data}\label{sec:empirical}
% nltk com machado, shakespeare e biblia
% arquivo de audio
% bytes quaisquer de algum arquivo?
% dados puxados da wikipedia, gmane ou ?
\section{Conclusions}\label{sec:conc}
\begin{acknowledgments}
	Financial support was obtained from CNPq (140860/2013-4,
	project 870336/1997-5), United Nations Development Program (contract: 2013/000566; project BRA/12/018) and FAPESP. 
	The authors are grateful to the American Jewish Committee for maintaining an online copy of the Adorno book used on the epigraph~\cite{adorno}, to GMANE creators and maintainers for the public email list data, to the communities of the email lists and other groups used in the analysis, and to the Brazilian Presidency of the Republic for keeping Participabr code and data open.
	We are also grateful to developers and users of Python scientific tools.
\end{acknowledgments}

### 2015-10-28 tables/tabNormNull.tex
feito benchmarking de diferencas

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 8 & 5 & 2 \\\hline
5.0 & 0.050 & 1.36 & 4 & 2 & 1 \\\hline
2.5 & 0.025 & 1.48 & 1 & 0 & 0 \\\hline
1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 1 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 normal distributions with $\mu=0$ and $\sigma=1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 normal distributions with $\mu=3$ and $\sigma=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7296$ and $\sigma(c_1')=0.2881$,
 $\mu(c_2')=0.6865$ and $\sigma(c_2')=0.2607$,
 $\mu(c_3')=0.6840$ and $\sigma(c_3')=0.2421$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 2 & 5 & 1 \\\hline
5.0 & 0.050 & 1.36 & 0 & 3 & 0 \\\hline
2.5 & 0.025 & 1.48 & 0 & 1 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 normal distributions with $\mu=0$ and $\sigma=1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 normal distributions with $\mu=3$ and $\sigma=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.6719$ and $\sigma(c_1')=0.2227$,
 $\mu(c_2')=0.7544$ and $\sigma(c_2')=0.2449$,
 $\mu(c_3')=0.6418$ and $\sigma(c_3')=0.2115$ .
}
\end{center}
\end{table}

### 2015-10-28 tables/tabUniformNull.tex
feito benchmarking de diferencas

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 10 & 1 & 5 \\\hline
5.0 & 0.050 & 1.36 & 6 & 0 & 3 \\\hline
2.5 & 0.025 & 1.48 & 4 & 0 & 1 \\\hline
1.0 & 0.010 & 1.63 & 2 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 2 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 1 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 uniform distributions within $[0,1)$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 uniform distributions within $[2,6)$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.8182$ and $\sigma(c_1')=0.3321$,
 $\mu(c_2')=0.7424$ and $\sigma(c_2')=0.2161$,
 $\mu(c_3')=0.7782$ and $\sigma(c_3')=0.2537$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 6 & 8 & 6 \\\hline
5.0 & 0.050 & 1.36 & 3 & 4 & 2 \\\hline
2.5 & 0.025 & 1.48 & 1 & 3 & 2 \\\hline
1.0 & 0.010 & 1.63 & 1 & 1 & 1 \\\hline
0.5 & 0.005 & 1.73 & 1 & 1 & 0 \\\hline
0.1 & 0.001 & 1.95 & 1 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 uniform distributions within $[0,1)$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 uniform distributions within $[2,6)$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.8010$ and $\sigma(c_1')=0.2810$,
 $\mu(c_2')=0.7471$ and $\sigma(c_2')=0.2921$,
 $\mu(c_3')=0.7612$ and $\sigma(c_3')=0.2608$ .
}
\end{center}
\end{table}

### 2015-10-28 tables/tabWeibullNull.tex
feito benchmarking de diferencas

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 0 & 5 & 5 & 3 \\\hline
5.0 & 0.050 & 1.36 & 0 & 2 & 0 & 1 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=0.1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.0682$ and $\sigma(c_1')=0.0454$,
 $\mu(c_2')=0.7361$ and $\sigma(c_2')=0.2594$,
 $\mu(c_3')=0.7231$ and $\sigma(c_3')=0.2350$ .
 $\mu(c_4')=0.6945$ and $\sigma(c_4')=0.2249$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 0 & 5 & 3 & 1 \\\hline
5.0 & 0.050 & 1.36 & 0 & 1 & 1 & 0 \\\hline
2.5 & 0.025 & 1.48 & 0 & 1 & 0 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=0.1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.0684$ and $\sigma(c_1')=0.0494$,
 $\mu(c_2')=0.7395$ and $\sigma(c_2')=0.2480$,
 $\mu(c_3')=0.7256$ and $\sigma(c_3')=0.2406$ .
 $\mu(c_4')=0.6831$ and $\sigma(c_4')=0.2130$ .
}
\end{center}
\end{table}
